Binary companions of red giant stars in \apogee\ \DR

### 2018-03-02 paper/1-catalog/twoface-catalog.tex
unimodal figure and caption

% Notebook: "HighK"
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-0}
\end{center}
\caption{%
Examples of stars in our high-$K$ sample, i.e. stars that likely have companions
(see \sectionname~\ref{sec:catalog-confident}), with different numbers of
visits.
Left panels show the data (black markers, error bars are the visit velocity
uncertainties) with 128 random orbits from the \nposterior\ posterior samples
under-plotted (grey lines); The \texttt{APOGEE\_ID} of each target and the
number of visits that pass our quality cuts, $N$, are indicated on each panel.
Right panels show the \nposterior\ posterior samples visualized in
period--eccentricity space.
In most cases, despite confidently having companions based on the RV amplitude,
the permitted orbit fits are highly multimodal.
\label{fig:highK-0}
}
\end{figure}

@@

% % Notebook: "TODO"
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{lowK}
% \end{center}
% \caption{%
% TODO
% \label{fig:lowK}
% }
% \end{figure}

@@

>>>>

% Notebook: "HighK"
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-0}
\end{center}
\caption{%
Examples of stars in our high-$K$ sample, i.e. stars that likely have companions
(see \sectionname~\ref{sec:catalog-confident}), with different numbers of
visits.
Left panels show the data (black markers, error bars are the visit velocity
uncertainties) with 128 random orbits from the \nposterior\ posterior samples
under-plotted (lines, blue); The \texttt{APOGEE\_ID} of each target and the
number of visits that pass our quality cuts, $N$, are indicated on each panel.
Right panels show the \nposterior\ posterior samples visualized in
period--eccentricity space.
In most cases, despite confidently having companions based on the RV amplitude,
the permitted orbit fits are highly multimodal.
\label{fig:highK-0}
}
\end{figure}

@@

% % Notebook: TODO
% \begin{figure}[hp]
% \begin{center}
% \includegraphics[width=\textwidth]{highK-unimodal}
% \end{center}
% \caption{%
% TODO
% \label{fig:highK-unimodal}
% }
% \end{figure}

@@

% Notebook: HighK-unimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Examples of high-$K$ stars with effectively unimodal posterior samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}
